---
title: "Final Assessment"
author: "John-Philipp Vogt"
date: "06/05/2022"
output: ioslides_presentation
---

# CoViD in Hamburg

## Objectives:

* Overview
  * Cases
  * Deaths
  * Daily Cases
  * Daily Deaths
  
* Mortality

```{r init, include=FALSE}

library(tidyverse)
library(gridExtra)

RKI_imptran <- function(x){
  read_csv(x, col_types = list(
    Altersgruppe = col_factor(),
    Geschlecht = col_factor(),
    IstErkrankungsbeginn = col_logical()
  )) %>%
    rename(geo_ID = IdLandkreis,age_group = Altersgruppe,
           sex = Geschlecht, rep_date = Meldedatum,
           ref_date = Refdatum, ref_rep_date = IstErkrankungsbeginn,
           amount_case = AnzahlFall, amount_death = AnzahlTodesfall,
           amount_recovery = AnzahlGenesen, new_case = NeuerFall,
           new_death = NeuerTodesfall, new_recovery = NeuGenesen)
}

RKI_geofil <- function(x, y){
  x %>% filter(geo_ID == y)
}

df_age_brackets_ref_date <- function(){
  A0 <- inf_HH %>% select(ref_date, age_group, amount_case) %>% 
    arrange(ref_date) %>% 
    group_by(ref_date, age_group) %>% 
    summarise(amount_case = sum(amount_case)) %>% 
    ungroup %>% 
    filter(age_group == "unbekannt") %>% 
    arrange(ref_date) %>% 
    mutate(cum_cases = cumsum(amount_case))
  
  A1 <- inf_HH %>% select(ref_date, age_group, amount_case) %>% 
    arrange(ref_date) %>% 
    group_by(ref_date, age_group) %>% 
    summarise(amount_case = sum(amount_case)) %>% 
    ungroup %>% 
    filter(age_group == "A00-A04") %>% 
    arrange(ref_date) %>% 
    mutate(cum_cases = cumsum(amount_case))
  
  A2 <- inf_HH %>% select(ref_date, age_group, amount_case) %>% 
    arrange(ref_date) %>% 
    group_by(ref_date, age_group) %>% 
    summarise(amount_case = sum(amount_case)) %>% 
    ungroup %>% 
    filter(age_group == "A05-A14") %>% 
    arrange(ref_date) %>% 
    mutate(cum_cases = cumsum(amount_case))
  
  A3 <- inf_HH %>% select(ref_date, age_group, amount_case) %>% 
    arrange(ref_date) %>% 
    group_by(ref_date, age_group) %>% 
    summarise(amount_case = sum(amount_case)) %>% 
    ungroup %>% 
    filter(age_group == "A15-A34") %>%
    arrange(ref_date) %>% 
    mutate(cum_cases = cumsum(amount_case))
  
  A4 <- inf_HH %>% select(ref_date, age_group, amount_case) %>% 
    arrange(ref_date) %>% 
    group_by(ref_date, age_group) %>% 
    summarise(amount_case = sum(amount_case)) %>% 
    ungroup %>% 
    filter(age_group == "A35-A59") %>%
    arrange(ref_date) %>% 
    mutate(cum_cases = cumsum(amount_case))
  
  A5 <- inf_HH %>% select(ref_date, age_group, amount_case) %>% 
    arrange(ref_date) %>% 
    group_by(ref_date, age_group) %>% 
    summarise(amount_case = sum(amount_case)) %>% 
    ungroup %>% 
    filter(age_group == "A60-A79") %>%
    arrange(ref_date) %>% 
    mutate(cum_cases = cumsum(amount_case))
  
  A6 <- inf_HH %>% select(ref_date, age_group, amount_case) %>% 
    arrange(ref_date) %>% 
    group_by(ref_date, age_group) %>% 
    summarise(amount_case = sum(amount_case)) %>% 
    ungroup %>% 
    filter(age_group == "A80+") %>%
    arrange(ref_date) %>% 
    mutate(cum_cases = cumsum(amount_case))
  
    rbind(A0, A1, A2, A3, A4, A5, A6)
}

df_age_brackets_rep_date <- function(){
  A0 <- inf_HH %>% select(rep_date, age_group, amount_case) %>% 
    arrange(rep_date) %>% 
    group_by(rep_date, age_group) %>% 
    summarise(amount_case = sum(amount_case)) %>% 
    ungroup %>% 
    filter(age_group == "unbekannt") %>% 
    arrange(rep_date) %>% 
    mutate(cum_cases = cumsum(amount_case))
  
  A1 <- inf_HH %>% select(rep_date, age_group, amount_case) %>% 
    arrange(rep_date) %>% 
    group_by(rep_date, age_group) %>% 
    summarise(amount_case = sum(amount_case)) %>% 
    ungroup %>% 
    filter(age_group == "A00-A04") %>% 
    arrange(rep_date) %>% 
    mutate(cum_cases = cumsum(amount_case))
  
  A2 <- inf_HH %>% select(rep_date, age_group, amount_case) %>% 
    arrange(rep_date) %>% 
    group_by(rep_date, age_group) %>% 
    summarise(amount_case = sum(amount_case)) %>% 
    ungroup %>% 
    filter(age_group == "A05-A14") %>% 
    arrange(rep_date) %>% 
    mutate(cum_cases = cumsum(amount_case))
  
  A3 <- inf_HH %>% select(rep_date, age_group, amount_case) %>% 
    arrange(rep_date) %>% 
    group_by(rep_date, age_group) %>% 
    summarise(amount_case = sum(amount_case)) %>% 
    ungroup %>% 
    filter(age_group == "A15-A34") %>%
    arrange(rep_date) %>% 
    mutate(cum_cases = cumsum(amount_case))
  
  A4 <- inf_HH %>% select(rep_date, age_group, amount_case) %>% 
    arrange(rep_date) %>% 
    group_by(rep_date, age_group) %>% 
    summarise(amount_case = sum(amount_case)) %>% 
    ungroup %>% 
    filter(age_group == "A35-A59") %>%
    arrange(rep_date) %>% 
    mutate(cum_cases = cumsum(amount_case))
  
  A5 <- inf_HH %>% select(rep_date, age_group, amount_case) %>% 
    arrange(rep_date) %>% 
    group_by(rep_date, age_group) %>% 
    summarise(amount_case = sum(amount_case)) %>% 
    ungroup %>% 
    filter(age_group == "A60-A79") %>%
    arrange(rep_date) %>% 
    mutate(cum_cases = cumsum(amount_case))
  
  A6 <- inf_HH %>% select(rep_date, age_group, amount_case) %>% 
    arrange(rep_date) %>% 
    group_by(rep_date, age_group) %>% 
    summarise(amount_case = sum(amount_case)) %>% 
    ungroup %>% 
    filter(age_group == "A80+") %>%
    arrange(rep_date) %>% 
    mutate(cum_cases = cumsum(amount_case))
  
  rbind(A0, A1, A2, A3, A4, A5, A6)
}

df_sex_ref_date <- function(){
  
  M <- inf_HH %>% select(ref_date, sex, amount_case) %>% 
    arrange(ref_date) %>% 
    group_by(ref_date, sex) %>% 
    summarise(amount_case = sum(amount_case)) %>% 
    ungroup %>% 
    filter(sex == "M") %>% 
    arrange(ref_date) %>% 
    mutate(cum_cases = cumsum(amount_case))

  W <- inf_HH %>% select(ref_date, sex, amount_case) %>% 
    arrange(ref_date) %>% 
    group_by(ref_date, sex) %>% 
    summarise(amount_case = sum(amount_case)) %>% 
    ungroup %>% 
    filter(sex == "W") %>% 
    arrange(ref_date) %>% 
    mutate(cum_cases = cumsum(amount_case))

  unbekannt <- inf_HH %>% select(ref_date, sex, amount_case) %>% 
    arrange(ref_date) %>% 
    group_by(ref_date, sex) %>% 
    summarise(amount_case = sum(amount_case)) %>% 
    ungroup %>% 
    filter(sex == "unbekannt") %>% 
    arrange(ref_date) %>% 
    mutate(cum_cases = cumsum(amount_case))

  df_sex_ref_date <- rbind(M, W, unbekannt)
}

df_sex_rep_date <- function(){
  
  M <- inf_HH %>% select(rep_date, sex, amount_case) %>% 
    arrange(rep_date) %>% 
    group_by(rep_date, sex) %>% 
    summarise(amount_case = sum(amount_case)) %>% 
    ungroup %>% 
    filter(sex == "M") %>% 
    arrange(rep_date) %>% 
    mutate(cum_cases = cumsum(amount_case))
  
  W <- inf_HH %>% select(rep_date, sex, amount_case) %>% 
    arrange(rep_date) %>% 
    group_by(rep_date, sex) %>% 
    summarise(amount_case = sum(amount_case)) %>% 
    ungroup %>% 
    filter(sex == "W") %>% 
    arrange(rep_date) %>% 
    mutate(cum_cases = cumsum(amount_case))
  
  unbekannt <- inf_HH %>% select(rep_date, sex, amount_case) %>% 
    arrange(rep_date) %>% 
    group_by(rep_date, sex) %>% 
    summarise(amount_case = sum(amount_case)) %>% 
    ungroup %>% 
    filter(sex == "unbekannt") %>% 
    arrange(rep_date) %>% 
    mutate(cum_cases = cumsum(amount_case))
  
  df_sex_rep_date <- rbind(M, W, unbekannt)
}

df_age_brackets_ref_date_deaths <- function(){
  A0 <- inf_HH %>% select(ref_date, age_group, amount_death) %>% 
    arrange(ref_date) %>% 
    group_by(ref_date, age_group) %>% 
    summarise(amount_death = sum(amount_death)) %>% 
    ungroup %>% 
    filter(age_group == "unbekannt") %>% 
    arrange(ref_date) %>% 
    mutate(cum_cases = cumsum(amount_death))
  
  A1 <- inf_HH %>% select(ref_date, age_group, amount_death) %>% 
    arrange(ref_date) %>% 
    group_by(ref_date, age_group) %>% 
    summarise(amount_death = sum(amount_death)) %>% 
    ungroup %>% 
    filter(age_group == "A00-A04") %>% 
    arrange(ref_date) %>% 
    mutate(cum_cases = cumsum(amount_death))
  
  A2 <- inf_HH %>% select(ref_date, age_group, amount_death) %>% 
    arrange(ref_date) %>% 
    group_by(ref_date, age_group) %>% 
    summarise(amount_death = sum(amount_death)) %>% 
    ungroup %>% 
    filter(age_group == "A05-A14") %>% 
    arrange(ref_date) %>% 
    mutate(cum_cases = cumsum(amount_death))
  
  A3 <- inf_HH %>% select(ref_date, age_group, amount_death) %>% 
    arrange(ref_date) %>% 
    group_by(ref_date, age_group) %>% 
    summarise(amount_death = sum(amount_death)) %>% 
    ungroup %>% 
    filter(age_group == "A15-A34") %>%
    arrange(ref_date) %>% 
    mutate(cum_cases = cumsum(amount_death))
  
  A4 <- inf_HH %>% select(ref_date, age_group, amount_death) %>% 
    arrange(ref_date) %>% 
    group_by(ref_date, age_group) %>% 
    summarise(amount_death = sum(amount_death)) %>% 
    ungroup %>% 
    filter(age_group == "A35-A59") %>%
    arrange(ref_date) %>% 
    mutate(cum_cases = cumsum(amount_death))
  
  A5 <- inf_HH %>% select(ref_date, age_group, amount_death) %>% 
    arrange(ref_date) %>% 
    group_by(ref_date, age_group) %>% 
    summarise(amount_death = sum(amount_death)) %>% 
    ungroup %>% 
    filter(age_group == "A60-A79") %>%
    arrange(ref_date) %>% 
    mutate(cum_cases = cumsum(amount_death))
  
  A6 <- inf_HH %>% select(ref_date, age_group, amount_death) %>% 
    arrange(ref_date) %>% 
    group_by(ref_date, age_group) %>% 
    summarise(amount_death = sum(amount_death)) %>% 
    ungroup %>% 
    filter(age_group == "A80+") %>%
    arrange(ref_date) %>% 
    mutate(cum_cases = cumsum(amount_death))
  
  rbind(A0, A1, A2, A3, A4, A5, A6)
}

df_age_brackets_rep_date_deaths <- function(){
  A0 <- inf_HH %>% select(rep_date, age_group, amount_death) %>% 
    arrange(rep_date) %>% 
    group_by(rep_date, age_group) %>% 
    summarise(amount_death = sum(amount_death)) %>% 
    ungroup %>% 
    filter(age_group == "unbekannt") %>% 
    arrange(rep_date) %>% 
    mutate(cum_cases = cumsum(amount_death))
  
  A1 <- inf_HH %>% select(rep_date, age_group, amount_death) %>% 
    arrange(rep_date) %>% 
    group_by(rep_date, age_group) %>% 
    summarise(amount_death = sum(amount_death)) %>% 
    ungroup %>% 
    filter(age_group == "A00-A04") %>% 
    arrange(rep_date) %>% 
    mutate(cum_cases = cumsum(amount_death))
  
  A2 <- inf_HH %>% select(rep_date, age_group, amount_death) %>% 
    arrange(rep_date) %>% 
    group_by(rep_date, age_group) %>% 
    summarise(amount_death = sum(amount_death)) %>% 
    ungroup %>% 
    filter(age_group == "A05-A14") %>% 
    arrange(rep_date) %>% 
    mutate(cum_cases = cumsum(amount_death))
  
  A3 <- inf_HH %>% select(rep_date, age_group, amount_death) %>% 
    arrange(rep_date) %>% 
    group_by(rep_date, age_group) %>% 
    summarise(amount_death = sum(amount_death)) %>% 
    ungroup %>% 
    filter(age_group == "A15-A34") %>%
    arrange(rep_date) %>% 
    mutate(cum_cases = cumsum(amount_death))
  
  A4 <- inf_HH %>% select(rep_date, age_group, amount_death) %>% 
    arrange(rep_date) %>% 
    group_by(rep_date, age_group) %>% 
    summarise(amount_death = sum(amount_death)) %>% 
    ungroup %>% 
    filter(age_group == "A35-A59") %>%
    arrange(rep_date) %>% 
    mutate(cum_cases = cumsum(amount_death))
  
  A5 <- inf_HH %>% select(rep_date, age_group, amount_death) %>% 
    arrange(rep_date) %>% 
    group_by(rep_date, age_group) %>% 
    summarise(amount_death = sum(amount_death)) %>% 
    ungroup %>% 
    filter(age_group == "A60-A79") %>%
    arrange(rep_date) %>% 
    mutate(cum_cases = cumsum(amount_death))
  
  A6 <- inf_HH %>% select(rep_date, age_group, amount_death) %>% 
    arrange(rep_date) %>% 
    group_by(rep_date, age_group) %>% 
    summarise(amount_death = sum(amount_death)) %>% 
    ungroup %>% 
    filter(age_group == "A80+") %>%
    arrange(rep_date) %>% 
    mutate(cum_cases = cumsum(amount_death))
  
  rbind(A0, A1, A2, A3, A4, A5, A6)
}

df_sex_ref_date_deaths <- function(){
  
  M <- inf_HH %>% select(ref_date, sex, amount_death) %>% 
    arrange(ref_date) %>% 
    group_by(ref_date, sex) %>% 
    summarise(amount_death = sum(amount_death)) %>% 
    ungroup %>% 
    filter(sex == "M") %>% 
    arrange(ref_date) %>% 
    mutate(cum_cases = cumsum(amount_death))
  
  W <- inf_HH %>% select(ref_date, sex, amount_death) %>% 
    arrange(ref_date) %>% 
    group_by(ref_date, sex) %>% 
    summarise(amount_death = sum(amount_death)) %>% 
    ungroup %>% 
    filter(sex == "W") %>% 
    arrange(ref_date) %>% 
    mutate(cum_cases = cumsum(amount_death))
  
  unbekannt <- inf_HH %>% select(ref_date, sex, amount_death) %>% 
    arrange(ref_date) %>% 
    group_by(ref_date, sex) %>% 
    summarise(amount_death = sum(amount_death)) %>% 
    ungroup %>% 
    filter(sex == "unbekannt") %>% 
    arrange(ref_date) %>% 
    mutate(cum_cases = cumsum(amount_death))
  
    rbind(M, W, unbekannt)
}

df_sex_rep_date_deaths <- function(){
  
  M <- inf_HH %>% select(rep_date, sex, amount_death) %>% 
    arrange(rep_date) %>% 
    group_by(rep_date, sex) %>% 
    summarise(amount_death = sum(amount_death)) %>% 
    ungroup %>% 
    filter(sex == "M") %>% 
    arrange(rep_date) %>% 
    mutate(cum_cases = cumsum(amount_death))
  
  W <- inf_HH %>% select(rep_date, sex, amount_death) %>% 
    arrange(rep_date) %>% 
    group_by(rep_date, sex) %>% 
    summarise(amount_death = sum(amount_death)) %>% 
    ungroup %>% 
    filter(sex == "W") %>% 
    arrange(rep_date) %>% 
    mutate(cum_cases = cumsum(amount_death))
  
  unbekannt <- inf_HH %>% select(rep_date, sex, amount_death) %>% 
    arrange(rep_date) %>% 
    group_by(rep_date, sex) %>% 
    summarise(amount_death = sum(amount_death)) %>% 
    ungroup %>% 
    filter(sex == "unbekannt") %>% 
    arrange(rep_date) %>% 
    mutate(cum_cases = cumsum(amount_death))
  
  rbind(M, W, unbekannt)
}

df_age_brackets_ref_date_recoveries <- function(){
  A0 <- inf_HH %>% select(ref_date, age_group, amount_recovery) %>% 
    arrange(ref_date) %>% 
    group_by(ref_date, age_group) %>% 
    summarise(amount_recovery = sum(amount_recovery)) %>% 
    ungroup %>% 
    filter(age_group == "unbekannt") %>% 
    arrange(ref_date) %>% 
    mutate(cum_cases = cumsum(amount_recovery))
  
  A1 <- inf_HH %>% select(ref_date, age_group, amount_recovery) %>% 
    arrange(ref_date) %>% 
    group_by(ref_date, age_group) %>% 
    summarise(amount_recovery = sum(amount_recovery)) %>% 
    ungroup %>% 
    filter(age_group == "A00-A04") %>% 
    arrange(ref_date) %>% 
    mutate(cum_cases = cumsum(amount_recovery))
  
  A2 <- inf_HH %>% select(ref_date, age_group, amount_recovery) %>% 
    arrange(ref_date) %>% 
    group_by(ref_date, age_group) %>% 
    summarise(amount_recovery = sum(amount_recovery)) %>% 
    ungroup %>% 
    filter(age_group == "A05-A14") %>% 
    arrange(ref_date) %>% 
    mutate(cum_cases = cumsum(amount_recovery))
  
  A3 <- inf_HH %>% select(ref_date, age_group, amount_recovery) %>% 
    arrange(ref_date) %>% 
    group_by(ref_date, age_group) %>% 
    summarise(amount_recovery = sum(amount_recovery)) %>% 
    ungroup %>% 
    filter(age_group == "A15-A34") %>%
    arrange(ref_date) %>% 
    mutate(cum_cases = cumsum(amount_recovery))
  
  A4 <- inf_HH %>% select(ref_date, age_group, amount_recovery) %>% 
    arrange(ref_date) %>% 
    group_by(ref_date, age_group) %>% 
    summarise(amount_recovery = sum(amount_recovery)) %>% 
    ungroup %>% 
    filter(age_group == "A35-A59") %>%
    arrange(ref_date) %>% 
    mutate(cum_cases = cumsum(amount_recovery))
  
  A5 <- inf_HH %>% select(ref_date, age_group, amount_recovery) %>% 
    arrange(ref_date) %>% 
    group_by(ref_date, age_group) %>% 
    summarise(amount_recovery = sum(amount_recovery)) %>% 
    ungroup %>% 
    filter(age_group == "A60-A79") %>%
    arrange(ref_date) %>% 
    mutate(cum_cases = cumsum(amount_recovery))
  
  A6 <- inf_HH %>% select(ref_date, age_group, amount_recovery) %>% 
    arrange(ref_date) %>% 
    group_by(ref_date, age_group) %>% 
    summarise(amount_recovery = sum(amount_recovery)) %>% 
    ungroup %>% 
    filter(age_group == "A80+") %>%
    arrange(ref_date) %>% 
    mutate(cum_cases = cumsum(amount_recovery))
  
  rbind(A0, A1, A2, A3, A4, A5, A6)
}

df_age_brackets_rep_date_recoveries <- function(){
  A0 <- inf_HH %>% select(rep_date, age_group, amount_recovery) %>% 
    arrange(rep_date) %>% 
    group_by(rep_date, age_group) %>% 
    summarise(amount_recovery = sum(amount_recovery)) %>% 
    ungroup %>% 
    filter(age_group == "unbekannt") %>% 
    arrange(rep_date) %>% 
    mutate(cum_cases = cumsum(amount_recovery))
  
  A1 <- inf_HH %>% select(rep_date, age_group, amount_recovery) %>% 
    arrange(rep_date) %>% 
    group_by(rep_date, age_group) %>% 
    summarise(amount_recovery = sum(amount_recovery)) %>% 
    ungroup %>% 
    filter(age_group == "A00-A04") %>% 
    arrange(rep_date) %>% 
    mutate(cum_cases = cumsum(amount_recovery))
  
  A2 <- inf_HH %>% select(rep_date, age_group, amount_recovery) %>% 
    arrange(rep_date) %>% 
    group_by(rep_date, age_group) %>% 
    summarise(amount_recovery = sum(amount_recovery)) %>% 
    ungroup %>% 
    filter(age_group == "A05-A14") %>% 
    arrange(rep_date) %>% 
    mutate(cum_cases = cumsum(amount_recovery))
  
  A3 <- inf_HH %>% select(rep_date, age_group, amount_recovery) %>% 
    arrange(rep_date) %>% 
    group_by(rep_date, age_group) %>% 
    summarise(amount_recovery = sum(amount_recovery)) %>% 
    ungroup %>% 
    filter(age_group == "A15-A34") %>%
    arrange(rep_date) %>% 
    mutate(cum_cases = cumsum(amount_recovery))
  
  A4 <- inf_HH %>% select(rep_date, age_group, amount_recovery) %>% 
    arrange(rep_date) %>% 
    group_by(rep_date, age_group) %>% 
    summarise(amount_recovery = sum(amount_recovery)) %>% 
    ungroup %>% 
    filter(age_group == "A35-A59") %>%
    arrange(rep_date) %>% 
    mutate(cum_cases = cumsum(amount_recovery))
  
  A5 <- inf_HH %>% select(rep_date, age_group, amount_recovery) %>% 
    arrange(rep_date) %>% 
    group_by(rep_date, age_group) %>% 
    summarise(amount_recovery = sum(amount_recovery)) %>% 
    ungroup %>% 
    filter(age_group == "A60-A79") %>%
    arrange(rep_date) %>% 
    mutate(cum_cases = cumsum(amount_recovery))
  
  A6 <- inf_HH %>% select(rep_date, age_group, amount_recovery) %>% 
    arrange(rep_date) %>% 
    group_by(rep_date, age_group) %>% 
    summarise(amount_recovery = sum(amount_recovery)) %>% 
    ungroup %>% 
    filter(age_group == "A80+") %>%
    arrange(rep_date) %>% 
    mutate(cum_cases = cumsum(amount_recovery))
  
  rbind(A0, A1, A2, A3, A4, A5, A6)
}

df_sex_ref_date_recoveries <- function(){
  
  M <- inf_HH %>% select(ref_date, sex, amount_recovery) %>% 
    arrange(ref_date) %>% 
    group_by(ref_date, sex) %>% 
    summarise(amount_recovery = sum(amount_recovery)) %>% 
    ungroup %>% 
    filter(sex == "M") %>% 
    arrange(ref_date) %>% 
    mutate(cum_cases = cumsum(amount_recovery))
  
  W <- inf_HH %>% select(ref_date, sex, amount_recovery) %>% 
    arrange(ref_date) %>% 
    group_by(ref_date, sex) %>% 
    summarise(amount_recovery = sum(amount_recovery)) %>% 
    ungroup %>% 
    filter(sex == "W") %>% 
    arrange(ref_date) %>% 
    mutate(cum_cases = cumsum(amount_recovery))
  
  unbekannt <- inf_HH %>% select(ref_date, sex, amount_recovery) %>% 
    arrange(ref_date) %>% 
    group_by(ref_date, sex) %>% 
    summarise(amount_recovery = sum(amount_recovery)) %>% 
    ungroup %>% 
    filter(sex == "unbekannt") %>% 
    arrange(ref_date) %>% 
    mutate(cum_cases = cumsum(amount_recovery))
  
  rbind(M, W, unbekannt)
}

df_sex_rep_date_recoveries <- function(){
  
  M <- inf_HH %>% select(rep_date, sex, amount_recovery) %>% 
    arrange(rep_date) %>% 
    group_by(rep_date, sex) %>% 
    summarise(amount_recovery = sum(amount_recovery)) %>% 
    ungroup %>% 
    filter(sex == "M") %>% 
    arrange(rep_date) %>% 
    mutate(cum_cases = cumsum(amount_recovery))
  
  W <- inf_HH %>% select(rep_date, sex, amount_recovery) %>% 
    arrange(rep_date) %>% 
    group_by(rep_date, sex) %>% 
    summarise(amount_recovery = sum(amount_recovery)) %>% 
    ungroup %>% 
    filter(sex == "W") %>% 
    arrange(rep_date) %>% 
    mutate(cum_cases = cumsum(amount_recovery))
  
  unbekannt <- inf_HH %>% select(rep_date, sex, amount_recovery) %>% 
    arrange(rep_date) %>% 
    group_by(rep_date, sex) %>% 
    summarise(amount_recovery = sum(amount_recovery)) %>% 
    ungroup %>% 
    filter(sex == "unbekannt") %>% 
    arrange(rep_date) %>% 
    mutate(cum_cases = cumsum(amount_recovery))
  
  rbind(M, W, unbekannt)
}
```

```{r load csv, include=FALSE}
inf_FRG <- RKI_imptran("/home/jpv/Documents/Uni/D.Proc.Vis/rStudioWD/covid_frg_project/SARS-CoV-2_Infektionen_in_Deutschland/Aktuell_Deutschland_SarsCov2_Infektionen.csv")

inf_HH <- RKI_geofil(inf_FRG, 2000)
```

```{r load csv2, include=FALSE}
inf_FRG_new_cases <- RKI_imptran("/home/jpv/Documents/Uni/D.Proc.Vis/rStudioWD/covid_frg_project/SARS-CoV-2_Infektionen_in_Deutschland/Archiv/all_new_cases.csv")
```

```{r filter csv, include=FALSE}
inf_HH_new_cases <- RKI_geofil(inf_FRG_new_cases, 2000)
```

## Overview :: Cases

### Cumulative Total of Confirmed Cases
```{r Cumulative Total of Confirmed Cases, echo=FALSE}
inf_HH %>%
  transmute(total_of_confirmed_cases = sum(amount_case)) %>%
  slice_tail()
```
## Overview :: Cases
```{r fig.align="center", echo=FALSE, fig.width=10}
inf_HH %>% select(ref_date, amount_case) %>%
  arrange(ref_date) %>% 
  group_by(ref_date) %>% 
  summarise(amount_case = sum(amount_case)) %>%
  mutate(cumulative_cases = cumsum(amount_case)) %>%
  ggplot(aes(ref_date, cumulative_cases)) + geom_area() +
  labs(x = "Time", y = "Cumulative Cases", title = "Cumulative Cases over Time") +
  scale_y_continuous(labels = function(x) format(x, scientific = FALSE)) +
  scale_x_date(date_breaks = "2 month", date_labels = "%m-%y")
```

## Overview :: Cases :: By Age Brackets

### Cumulative Total of Confirmed Cases by Age Bracket
```{r echo=FALSE}
inf_HH %>%
  group_by(age_group) %>% 
  transmute(total_of_confirmed_cases = cumsum(amount_case)) %>%
  slice_tail() %>% 
  arrange(desc(total_of_confirmed_cases))
```

## Overview :: Cases :: By Age Brackets

```{r include=FALSE}
AAll_ref_date <- df_age_brackets_ref_date()
```
```{r fig.align="center", echo=FALSE, fig.width=10}

AAll_ref_date %>% ggplot(aes(x = ref_date, y = cum_cases, fill = age_group)) + geom_area() +
  labs(x = "Time", y = "Cumulative Cases", fill = "Age Brackets", title = "Cumulative Cases over Time by Age Bracket") +
  scale_y_continuous(labels = function(x) format(x, scientific = FALSE)) +
  scale_x_date(date_breaks = "2 month", date_labels = "%m-%y")

AAllplot_ref_date <- AAll_ref_date %>% ggplot(aes(x = ref_date, y = cum_cases, fill = age_group)) + geom_area(show.legend = FALSE)
```

## Overview :: Cases :: By Age Brackets

```{r fig.align="center", echo=FALSE, fig.width=10}
inf_HH %>% select(age_group, amount_case) %>%
  group_by(age_group) %>%
  summarise(sum = sum(amount_case)) %>%
  ggplot(aes(fct_reorder(age_group, sum), sum)) + geom_col() +
  labs(x = "Age Brackets", y = "Sum of Cases", title = "Sum of Cases by Age Bracket")
```

## Overview :: Cases :: By Sex

### Total of Confirmed Cases by Sex

```{r echo=0}
inf_HH %>%
  group_by(sex) %>% 
  transmute(total_of_confirmed_cases = cumsum(amount_case)) %>%
  slice_tail() %>% 
  arrange(desc(total_of_confirmed_cases))
```

## Overview :: Cases :: By Sex

```{r include=FALSE}
sex_ref_date <- df_sex_ref_date()
```
```{r fig.align="center", echo=FALSE, fig.width=10}
sex_ref_date %>% ggplot(aes(x = ref_date, y = cum_cases, fill = sex)) + geom_area() +
  labs(x = "Time", y = "Cumulative Cases", fill = "Age Brackets", title = "Cumulative Cases over Time by Sex") +
  scale_y_continuous(labels = function(x) format(x, scientific = FALSE)) +
  scale_x_date(date_breaks = "2 month", date_labels = "%m-%y")

sexplot_ref_date <- sex_ref_date %>% ggplot(aes(x = ref_date, y = cum_cases, fill = sex)) + geom_area(show.legend = FALSE)
```

## Overview :: Deaths

```{r echo=FALSE}
inf_HH %>%
  transmute(total_of_confirmed_deaths = cumsum(amount_death)) %>%
  slice_tail()
```

## Overview :: Deaths

```{r fig.align="center", echo=FALSE, fig.width=10}
inf_HH %>% select(ref_date, amount_death) %>%
  arrange(ref_date) %>% 
  group_by(ref_date) %>% 
  summarise(amount_death = sum(amount_death)) %>%
  mutate(cumulative_deaths = cumsum(amount_death)) %>%
  ggplot(aes(ref_date, cumulative_deaths)) + geom_area() +
  labs(x = "Time", y = "Cumulative Deaths", title = "Cumulative Deaths over Time") +
  scale_y_continuous(labels = function(x) format(x, scientific = FALSE)) +
  scale_x_date(date_breaks = "2 month", date_labels = "%m-%y")
```

## Overview :: Deaths :: By Age Bracket

```{r echo=FALSE}
inf_HH %>% 
  group_by(age_group) %>% 
  transmute(total_of_confirmed_deaths = cumsum(amount_death)) %>%
  slice_tail() %>% 
  arrange(desc(total_of_confirmed_deaths))
```

## Overview :: Deaths :: By Age Bracket

```{r include=FALSE}
AAll_ref_date_deaths <- df_age_brackets_ref_date_deaths()
```
```{r fig.align="center", echo=FALSE, fig.width=10}
AAll_ref_date_deaths %>% ggplot(aes(x = ref_date, y = cum_cases, fill = age_group)) + geom_area() +
  labs(x = "Time", y = "Cumulative Deaths", fill = "Age Bracket", title = "Cumulative Deaths over Time By Age Bracket") +
  scale_x_date(date_breaks = "2 month", date_labels = "%m-%y")

AAllplot_ref_date_deaths <- AAll_ref_date_deaths %>% ggplot(aes(x = ref_date, y = cum_cases, fill = age_group)) + geom_area(show.legend = FALSE)
```

## Overview :: Deaths :: By Age Bracket

```{r fig.align="center", echo=FALSE, fig.width=10}
inf_HH %>% select(age_group, amount_death) %>%
  group_by(age_group) %>%
  summarise(sum = sum(amount_death)) %>%
  ggplot(aes(fct_reorder(age_group, sum), sum)) + geom_col() +
  labs(x = "Time", y = "Cumulative Deaths", fill = "Age Bracket", title = "Cumulative Deaths over Time By Age Bracket")
```

## Overview :: Deaths :: By Sex

```{r echo=FALSE}
inf_HH %>%
  group_by(sex) %>% 
  transmute(total_of_confirmed_deaths = cumsum(amount_death)) %>%
  slice_tail() %>% 
  arrange(desc(total_of_confirmed_deaths))
```

## Overview :: Deaths :: By Sex

```{r include=FALSE}
sex_ref_date_deaths <- df_sex_ref_date_deaths()
```
```{r fig.align="center", echo=FALSE, fig.width=10}
sex_ref_date_deaths %>% ggplot(aes(x = ref_date, y = cum_cases, fill = sex)) + geom_area() +
  labs(x = "Time", y = "Cumulative Deaths", fill = "Age Bracket", title = "Cumulative Deaths over Time By Sex") +
  scale_x_date(date_breaks = "2 month", date_labels = "%m-%y")

sexplot_ref_date_deaths <- sex_ref_date_deaths %>% ggplot(aes(x = ref_date, y = cum_cases, fill = sex)) + geom_area(show.legend = FALSE)
```

## Daily Cases

```{r fig.align="center", echo=FALSE, fig.width=10}
inf_HH %>% select(ref_date, new_case, amount_case) %>% 
    filter(new_case != -1) %>% 
    group_by(ref_date) %>% 
    summarise(daily_cases = sum(amount_case)) %>% 
    ggplot(aes(ref_date, daily_cases)) + geom_area() +
    labs(x = "Time", y = "Cases", title = "New Cases per Day") +
    scale_x_date(date_breaks = "2 month", date_labels = "%m-%y")
```

## Daily Deaths

```{r fig.align="center", echo=FALSE, fig.width=10}
inf_HH %>% select(ref_date, amount_death) %>% 
    filter(amount_death != 0) %>% 
    group_by(ref_date) %>% 
    summarise(daily_deaths = sum(amount_death)) %>%
    ggplot(aes(ref_date, daily_deaths)) + geom_area() +
    labs(x = "Time", y = "Deaths", title = "New Deaths per Day") +
    scale_x_date(date_breaks = "2 month", date_labels = "%m-%y")
```

## Mortality

```{r include=FALSE}
cases_age <- inf_HH %>%
  group_by(age_group) %>% 
  transmute(total_of_confirmed_cases = cumsum(amount_case)) %>%
  slice_tail()

deaths_age <- inf_HH %>% 
  group_by(age_group) %>% 
  transmute(total_of_confirmed_deaths = cumsum(amount_death)) %>%
  slice_tail()

mort <- bind_cols(cases_age, deaths_age)
```

``` {r include=FALSE}
mort %>% 
  mutate(mortality_in_percent = (total_of_confirmed_deaths / total_of_confirmed_cases)*100) %>% 
  arrange(desc(total_of_confirmed_deaths)) %>% 
  select(age_group...1, total_of_confirmed_deaths, mortality_in_percent)

mort_fin <- mort %>% 
  mutate(mortality_in_percent = (total_of_confirmed_deaths / total_of_confirmed_cases)*100) %>% 
  select(age_group...1, total_of_confirmed_deaths, mortality_in_percent)

male_deaths <- inf_HH %>% 
  select(age_group, sex, amount_death) %>% 
  filter(sex == "M") %>% 
  group_by(age_group) %>% 
  summarise(death_sex_M = sum(amount_death))

female_deaths <- inf_HH %>% 
  select(age_group, sex, amount_death) %>% 
  filter(sex == "W") %>% 
  group_by(age_group) %>% 
  summarise(death_sex_W = sum(amount_death))

mort_fin_sex <- bind_cols(mort_fin, male_deaths, female_deaths)

mort_fin_sex <- mort_fin_sex %>%
    select(age_group...1, total_of_confirmed_deaths, mortality_in_percent, death_sex_M, death_sex_W)

mort_fin_sex_final <- mort_fin_sex %>% 
    mutate(Male_Share = (death_sex_M / total_of_confirmed_deaths)*100) %>% 
    mutate(Female_Share = (death_sex_W / total_of_confirmed_deaths)*100) %>% 
    rename(Age_Bracket = age_group...1, Death_Toll = total_of_confirmed_deaths, Mortality = mortality_in_percent, Male_Deaths = death_sex_M, Female_Deaths = death_sex_W)
```

```{r echo=FALSE}
mort_fin_sex %>% 
    mutate(Male_Share = (death_sex_M / total_of_confirmed_deaths)*100) %>% 
    mutate(Female_Share = (death_sex_W / total_of_confirmed_deaths)*100) %>% 
    rename(Ages = age_group...1, Death_Toll = total_of_confirmed_deaths, Mortality = mortality_in_percent, Male_Deaths = death_sex_M, Female_Deaths = death_sex_W) %>% 
    arrange(desc(Mortality))
```

## What I have learned

* Data Science and Visualisation basics
* Basics for statistical analysis
* Querying Data with R - the tidyverse mostly
* basics in .(R)md
* basics for AWK
* basics in git

## Final Slide

### Sources:
  * https://github.com/robert-koch-institut/SARS-CoV-2_Infektionen_in_Deutschland
  * https://github.com/digitalIceCream/rStudio-CoViD-Project